\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 (February 5) and the Final documentation; the contributions prior to Rev0 are
NOT included.

Due to project requirements, the actual cut-off date will be March 20, 2026.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Awurama & 2\\
Fei & 3\\
Ghena & 5\\
Haniye & 5\\

\bottomrule
\end{tabular}
\end{table}

Two team meetings were for the development subteam only (Ghena + Haniye).

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } Dr. Spencer Smith

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Awurama & 2\\
Fei & 2\\
Ghena & 2\\
Haniye & 2\\
\bottomrule
\end{tabular}
\end{table}
Each subteam had an individual meeting with the supervisor. A single meeting with a stakeholder was held for the whole team.
\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Awurama & 0\\
Fei & 1\\
Ghena & 0\\
Haniye & 0\\

\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } Tanya Djavaherpour

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Awurama & 1\\
Fei & 1\\
Ghena & 1\\
Haniye & 1\\

\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & Num & 100\% \\
Name 1 & Num & \% \\
Name 2 & Num & \% \\
Name 3 & Num & \% \\
Name 4 & Num & \% \\
Name 5 & Num & \% \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.  For
instance, if a team member has more commits to unmerged branches, these numbers
can be provided here.  If multiple people contribute to a commit, git allows for
multi-author commits.}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Name 1 & Num & Num \\
Name 2 & Num & Num \\
Name 3 & Num & Num \\
Name 4 & Num & Num \\
Name 5 & Num & Num \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Team Charter Trigger Items}
\subsection{Summary of Triggers}
\begin{enumerate}
\item{Attending every weekly Monday virtual meeting during lecture time when there are no lectures. Unless the whole team decides to cancel}
\item{Team members expected to attend all meetings on time, fully prepared and having reviewed relevant materials and the agenda for the meeting}
\item{All deliverables must meet the team's agreed-upon standards}
\item{Deliverables must be reviewed by all assigned team members through the "reviewed" confirmation on GitHub, before deliverables are ready to be merged.}
\item{Feedback on deliverables and revisions must be made within 24 hours}
\end{enumerate}

\subsection{Trigger Violations}
\textbf{Trigger:} All deliverables must meet the team's agreed-upon standards \\
\textbf{Comments:} Deliverables did not meet expected standards, and communication on the status of deliverables were lacking.\\
\subsection{Next Step Plans}
As previously mentioned in the productivity report for \href{https://github.com/thaafei/DomainX/blob/main/docs/projMngmnt/POC_Team_Contrib.pdf}{POC}, the next for triggers that are reoccurring was by contacting the supervisor and TA for help.
After discussion, the team was able to work much better as the underlying problem causing the issue was identified and resolved.

\end{document}