\documentclass[final,1p,times,authoryear,12pt]{elsarticle}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

\usepackage{longtable}
\usepackage{paralist}
\usepackage{booktabs}
\usepackage{float}
\restylefloat{table}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
%\usepackage{geometry}
\usepackage{pdflscape}
\usepackage{color}
\usepackage{xcolor} 
\usepackage{xspace}
\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{wrapfig}
\providecommand{\wss}[1]{\textcolor{blue}{\textit{#1}}}

\begin{document}
\begin{frontmatter}

\title{State of the Practice for Open-Source Neural Network Software}
\address{Department of Computing and Software \\
McMaster University \\
Hamilton, Ontario, Canada}

\begin{abstract}
% \wss{150--250 word abstract: problem/gap, method (measurement template + repo metrics + AHP),
%  headline results, contributions (DomainX tool + dataset + findings). 
%  one-line pointer to the DomainX repo and a brief data availability statement.}

Neural network (NN) libraries underpin modern research and production AI systems, yet their software-engineering practices vary 
widely and are rarely assessed in a transparent, reproducible way. Existing comparisons are often ad hoc, relying on manual 
checklists and spreadsheets that are difficult to audit and update as repositories evolve. 
We present DomainX, a tool-supported workflow for conducting a state-of-practice assessment of NN software based on a published
 methodology. DomainX centralizes evidence capture from public artifacts (documentation, tests, issue trackers, releases, and CI pipelines),
  supports scoring via a measurement template across nine software-quality attributes, and incorporates repository-based measures extracted from public repositories. 
  Using these inputs, DomainX computes an overall comparison using the Analytic Hierarchy Process (AHP) and exports traceable assessment artifacts. 
  We apply the workflow to a curated shortlist of 28 open-source NN software packages, producing a traceable dataset of template responses, measures, 
  and package-level references (project website and repository URLs), along with an evidence-based ranking and per-quality breakdowns. A companion repository provides the tool and assessment artifacts to support review 
  and reuse.
\end{abstract}

\begin{keyword}
% \wss{state of practice; research software; NLP libraries; software quality;
%  measurement template; AHP; reproducibility; traceability.}
state of practice; research software; neural network libraries; software quality;
measurement template; Analytic Hierarchy Process (AHP); traceability; reproducibility; repository mining.
\end{keyword}

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \wss{why software quality matters for research/engineering outcomes 
% and why a state-of-practice assessment is useful for the domain.
%   why assessment is difficult in practice (evidence scattered across docs/tests/issues/CI,
%    manual spreadsheet workflows are time-consuming and hard to audit/reproduce).}

% \wss{State contributions explicitly as a short bullet list: DomainX tool support (include repo pointer), ffinal shortlist + completed dataset,
%  ranking + sensitivity analysis + insights/recommendations.}

% \wss{ short paragraph that states what software is being evaluated: 
% the set of open-source packages in the selected domain, what they generally do, the final shortlist size,
%  and a pointer to the appendix/table listing the packages.}

% \wss{ roadmap of the remainder of the paper.}

Research and engineering outcomes increasingly depend on software, and the quality of that software affects reliability,
 maintainability, and reproducibility. In domains where open-source libraries are widely reused,
  understanding current development practice is a prerequisite for improving it. A \emph{state-of-practice} assessment provides
   a structured way to characterize what developers commonly do in a domain by evaluating representative software packages against 
   explicit software-quality criteria using traceable evidence.

Conducting such assessments rigorously is challenging in practice. Evidence relevant to software quality is distributed across many 
public artifacts, including documentation, tutorials, repository history, tests, issue trackers, releases, and continuous integration 
(CI) configurations. As a result, assessments are often performed using manual spreadsheet-based workflows with ad hoc scoring 
and limited traceability, making the process time-consuming, difficult to audit, and hard to reproduce as repositories evolve.

This paper presents a tool-supported state-of-practice assessment for \emph{neural network (NN) software}. 
The target audience is developers and maintainers of NN software; accordingly, the scope is restricted to NN packages rather than 
general-purpose NN-supporting libraries from adjacent communities. The assessment workflow follows a published state-of-practice 
methodology based on (i) a measurement template organized by software-quality attributes, (ii) repository-based measures extracted 
from public repositories, and (iii) an Analytic Hierarchy Process (AHP) ranking procedure to combine evidence into transparent 
comparisons.

The contributions of this work are:
\begin{itemize}
  \item A curated shortlist of 28 open-source NN software packages evaluated using a consistent, evidence-based procedure (Appendix~\ref{app-packages}).
  \item A traceable assessment dataset recording measurement-template responses, repository-based measures, and associated evidence links for auditability and reuse.
  \item DomainX, a tool that supports evidence capture, scoring, ranking computations, and export of results to reduce manual effort and improve traceability (\url{https://github.com/thaafei/DomainX}).
\end{itemize}

The remainder of this paper defines key concepts and summarizes background (Section~\ref{background}), describes the assessment methodology and tool support (Section~\ref{methods}), 
and reports results and observations from applying the approach to the shortlisted packages (Section~\ref{results}).
 The paper concludes with discussion, recommendations, and limitations (Sections~\ref{discussion}--\ref{conclusion}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background and Definitions} \label{background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \wss{Define key terms: research software, domain, library/package,
%  and evidence (public artifacts such as docs, repository history, issues, tests, CI configs).
%    state-of-the-art vs state-of-practice and why gaps occur.}

% \wss{brief overview of the assessment methodology being followed (cite the methodology paper)
%  and  short explanation of AHP and why it is used for ranking in this context.}
%%CITE THE METHODOLOGY PAPERRR

In this paper, \emph{research software} refers to software used to support scientific or engineering work such as data processing,
 model training or inference, experimentation, and analysis. A \emph{domain} is a coherent problem area characterized by 
 shared goals and typical workflows; in a state-of-practice assessment, the domain determines which software packages are 
 relevant and what evidence is meaningful for evaluation. A \emph{library} (or package) is a reusable software component intended
  to be integrated into other programs. We use \emph{evidence} to mean publicly available artifacts that indicate software-development
   practice, including documentation and tutorials, repository history (commits and releases), issue trackers and pull requests,
    tests, and continuous integration (CI) configurations.

The \emph{state of the art} describes the most advanced methods and recommended best practices reported in research and practitioner
 literature. The \emph{state of practice} describes what is commonly done in real projects: the tools used, the artifacts produced,
  and the quality-related practices that are routinely applied. Gaps between state of the art and state of practice are common,
   particularly in research settings where incentives and timelines may prioritize functionality and 
   novelty over long-term maintainability, transparency, or reproducibility. 
   A state-of-practice assessment aims to characterize this reality using explicit criteria and traceable evidence,
    enabling systematic comparison and targeted recommendations.

A published state-of-practice methodology guides our assessment by combining (i) a measurement template grounded in software-quality
 attributes with (ii) evidence extracted from public artifacts and repository-based measures, enabling comparisons that are intended 
 to be reproducible and auditable. %%don't forget to actually cite the paper

To produce an overall comparison across multiple criteria, we use the Analytic Hierarchy Process (AHP), 
a multi-criteria decision-making method that derives weights from pairwise comparisons of criteria and aggregates scores accordingly. 
AHP is well suited to this setting because it makes weighting assumptions explicit and supports transparent trade-offs
 among software-quality attributes. In this work, AHP is used to compute an evidence-based ranking and to support sensitivity analysis
  on how rankings change under different weighting choices.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}\label{methods}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Domain framing and scope}\label{scope}
% \wss{Define the assessed domain, what is in scope vs out of scope for “NN software” in this assessment. 
% Include inclusion/exclusion criteria (public repo, docs, relevant functionality, examples).}

Neural network (NN) software is defined here as open-source libraries whose primary purpose is to enable the development, 
training, deployment, analysis, or direct use of neural network models. The target audience for this assessment is developers
 and maintainers of NN software. Accordingly, general-purpose NN-supporting packages
 (e.g., numerical computing, data manipulation, or plotting libraries) are out of scope because they belong to different developer 
 communities and would confound interpretation of NN software development practice. 
 Packages are included when they have a publicly accessible repository and sufficient publicly available artifacts 
 (e.g., documentation and repository history) to support evidence-based evaluation.

\subsection{Candidate identification and filtering}\label{filtering}
% \wss{Describe how candidates were identified (sources/search style) , how filtering produced the final set.
%  Report counts at each step and the final shortlist size. Final shortlist: 28. 
%  Point to Appendix~\ref{app-packages} for the full list and exclusions (see emails).}

 Candidate packages were compiled by aggregating package names from authoritative sources and normalizing duplicates 
 and naming variants. To align the assessment with the intended audience, packages that were NN-supporting rather than NN software 
 were removed. Following supervisor guidance, NN software packages were retained even when they appeared only once across the
  authoritative sources to prioritize completeness of coverage. The final shortlist contains 28 packages. 
  The full shortlist and excluded candidates (with brief reasons) are provided in Appendix~\ref{app-packages}.

\subsection{Evidence sources and data collection}\label{data}
% \wss{Describe evidence sources used to score each package: 
% documentation/README, tutorials/examples, repository history, releases, issues/PRs, tests, CI/CD configuration. 
%  automated extraction vs manual inspection (repo metrics vs others). 
%   how evidence was recorded to make results traceable and auditable? (metrics spreadsheet)}

Evidence was derived from publicly available artifacts associated with each package, 
including documentation (e.g., README and installation guides), tutorials/examples, 
repository history, releases, issue trackers and pull requests, tests, and continuous integration (CI) configuration when available. 
Repository-based measures were extracted using automated scripts/tools. Some measurement-template questions required manual
 judgment (e.g., installation and usage guidance, presence of tests, or CI configuration). 
 Responses were recorded directly in the measurement template, and each package entry includes a project website URL and a source-code 
 repository URL that can be used to verify the recorded responses against the corresponding public artifacts.

\subsection{Measurement template and scoring}\label{template}
% \wss{the assessment uses the methodology paper’s measurement template organized by software qualities. 
% Qualities assessed: installability, correctness \& verifiability, surface reliability, surface robustness, surface usability, 
% maintainability, reusability, surface understandability, visibility/transparency. 
%  scoring approach summary (evidence $\rightarrow$ question response $\rightarrow$ normalized score $\rightarrow$ aggregation). 
%   rules for missing/unclear evidence and any consistency checks.}

The assessment uses a published measurement template organized by software-quality attributes. 
The qualities assessed are: installability; correctness and verifiability; surface reliability; surface robustness; surface usability;
 maintainability; reusability; surface understandability; and visibility/transparency. 
 For each package, publicly available evidence was used to answer template questions and derive per-quality scores according 
 to the template’s scoring rules. Scores were normalized and aggregated to support cross-package comparison.
  When evidence was missing or ambiguous, responses were recorded conservatively and flagged for traceability.

\subsection{Repository-based measures}\label{metrics}
\wss{Describe repository/empirical measures collected (e.g. GitHub-based measures + codebase statistics). 
 the tools/sources used (e.g., GitHub API, scc, git\_stats) and what each category captures. 
  enough detail to reproduce extraction.}

\subsection{Ranking method (AHP) and sensitivity analysis}\label{ahp}
%%Ghena
\wss{Explain how AHP was used to compute weights and produce an overall ranking from quality scores. 
Describe how pairwise comparisons were obtained and how final scores were computed. 
 sensitivity analysis results (plan if not yet complete) to assess ranking stability under reasonable weight changes. 
 ranking supports comparison/insight rather than a universal claim of “best.”}

\subsection{Tool support: DomainX}\label{domainx}
\wss{ DomainX at the key-feature level: centralized evidence capture, structured template completion, 
metric extraction, AHP computation, and export of results.  reduced manual effort and improved traceability/auditability. 
Repository: \url{https://github.com/thaafei/DomainX} }

%%add snapshot

\subsection{Environment and reproducibility}\label{env}
%%Fei
\wss{Describe the evaluation environment and  steps to take for reproducing (e.g. pinned versions, standardized install attempts). 
Mention Dockerfiles used for older packages where needed and connect this to repeatability and transparency.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Descriptive summary of assessed packages}\label{results-summary}
\wss{Summarize the evaluated set (final no., alive/dead counts, languages/activity/licensing if reported). 
Present  statistics that help give insight into the domain landscape before ranking.}

\subsection{Overall ranking}\label{results-ranking}
\wss{ the final ranking table and a short explanation of how to read it. 
Highlight  top-ranked packages without overconfidence/ overdoing it. Reference DomainX ranking output as a figure/table.}

\subsection{Quality-by-quality breakdown}\label{results-byquality}
\wss{ results by quality attribute (tables/figures). Identify strong/weak packages per quality and report domain-wide patterns
 supported by evidence.}

\subsection{Sensitivity analysis}\label{results-sensitivity}
\wss{ how rankings change under weight variation, identify stable vs unstable parts of the ranking and summary of implications.}

\subsection{Popularity vs evidence-based ranking (optional)}\label{results-popularity}
\wss{Compare evidence-based results against reputation indicators (e.g. stars/download). Discuss alignment/misalignment
 and what it suggests about state-of-practice versus  popularity.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Recommendations}\label{discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\wss{ what the results imply for users and maintainers. 
 actionable recommendations organized by quality attribute (installability, maintainability, transparency...). 
 Keep recommendations evidence-backed.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Threats to Validity and Limitations}\label{validity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\wss{ construct validity, internal validity, external validity, and temporal validity. 
Note limitations such as evolving repositories, subjectivity in scoring, missing/ambiguous evidence,
 and interviews not conducted yet.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Work}\label{conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\wss{Summarize contributions (DomainX + dataset + findings), key results,  list future work 
(interviews, expanded shortlist, stronger sensitivity analysis, refined scoring rules, deeper automation).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Assessed packages and exclusions}\label{app-packages}
\wss{table listing all assessed packages and excluded candidates with brief reasons to help traceability.}

\section{Measurement template excerpt and scoring rules}\label{app-template}
\wss{compact excerpt of measurement template and key scoring/normalization rules, or provide link to full template.}

\section{AHP weights and matrices}\label{app-ahp}
\wss{ final AHP weights and any matrices needed for transparency and reproducibility.}

\section{DomainX screenshots and exported artifacts}\label{app-tool}
\wss{potential figures: ranking view, table view, metric editing view, export example. }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\end{document}