\documentclass[12pt, titlepage]{article}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{url}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}
\usepackage{mdframed}
\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname}
\author{\authname}
\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
March 6 & Rev 1 & First copy of VnV Report done by the whole team\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l}
  \toprule
  \textbf{symbol} & \textbf{description}\\
  \midrule
  T & Test\\
  \bottomrule
\end{tabular}\\

\noindent\textit{All additional terms conform to those defined in the \href{https://github.com/thaafei/DomainX/blob/main/docs/SRS/SRS.pdf}{SRS} Glossary (Section~4.1).}
\newpage

\tableofcontents

\listoftables %if appropriate

\newpage

\pagenumbering{arabic}
This document is the Verification and Validation report based on the tests identified from the \href{https://github.com/thaafei/DomainX/blob/main/docs/VnVPlan/VnVPlan.pdf}{Cerification and Validation plan}.

\section{Functional Requirements Evaluation}
\hspace{2em}This section presents the results of the functional tests defined in the project's
Verification and Validation (VnV) Plan. These tests verify that the implemented system
satisfies the functional requirements specified in the Software Requirements Specification
(SRS). The tests are organized according to the system's main feature areas.

\subsection{User Authentication and Profile Management}
\hspace{2em}The test results below verify that users can successfully authenticate
and manage their account information within the system. These tests ensure that
login, profile updates, and password modification operate correctly while
restricting access to authorized users only.

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--AC--1
\vspace{0.4em}

\textbf{Input:} Submission of valid sign-up information through the system interface.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that a new user account is created successfully and the user is redirected to the login page.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that a new user account is created successfully and the user is redirected to the login page.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR2
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--AC--2
\vspace{0.4em}

\textbf{Input:} Submission of valid login credentials through the system login interface.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the user enters valid login credentials and is redirected to the system dashboard.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the user enters valid login credentials and is redirected to the system dashboard.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):}  FR3
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--AC--3
\vspace{0.4em}

\textbf{Input:} A user with the Contributor role logs into the system and attempts to edit metric values in the interactive data table.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the user is able to view library data and successfully edit metric values in the interactive table.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the user is able to view library data and successfully edit metric values in the interactive table.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} SR--AC2
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--AC--4
\vspace{0.4em}

\textbf{Input:} A user with the Super Admin role logs into the system and attempts to access administrative functionality for managing users.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the user is able to access administrative functionality and manage user accounts within the system.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the user is able to access administrative functionality and manage user accounts within the system.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} SR--AC2
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--AC--5
\vspace{0.4em}

\textbf{Input:} Submission of invalid login credentials or an unregistered email through the system login interface.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that access is denied, an Invalid credentials error message is displayed, and no session token is created.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that access is denied, an Invalid credentials error message is displayed, and no session token is created.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} SR--AC5, UH--UP3, LF--AR6
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--AC--6
\vspace{0.4em}

\textbf{Input:} A Super Admin updates the role of an existing user (e.g., Contributor to Super Admin) through the user management interface.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the user role is updated successfully and the interface updates to reflect the new permissions associated with the role.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the user role is updated successfully and the interface updates to reflect the new permissions associated with the role.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} SR--AC4, PR--SC3, FR7
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--AC--7
\vspace{0.4em}

\textbf{Input:} An authenticated user accesses their profile page and submits a request to change their password using the password update form.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the user password is updated successfully and the new password is required for subsequent logins.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the user password is updated successfully and the new password is required for subsequent logins.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} SR--AC5, PR--SC1
\end{mdframed}


\subsection{Domain and Data Management}

\hspace{2em}The following tests verify that domains, libraries, and metrics
can be created, modified, and stored correctly within the system. These
tests ensure that domain data management and metric updates function as
expected.

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--DM--1
\vspace{0.4em}

\textbf{Input:} A Super Admin submits valid domain information through the domain creation interface.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the new domain is created successfully, appears in the system interface, and is stored in the database with a unique identifier.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the new domain is created successfully, appears in the system interface, and is stored in the database with a unique identifier.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--5, SR--INT1, SR--AC3
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--DM--2
\vspace{0.4em}

\textbf{Input:} A Contributor or Super Admin adds a library to a domain by providing a valid GitHub repository URL.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the library is added successfully and repository metadata (e.g., commits, issues, lines of code, etc.) is automatically retrieved using GitHub API, SCC, and GitStats without errors.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the library is added successfully and repository metadata (e.g., commits, issues, lines of code, etc.) is automatically retrieved using GitHub API, SCC, and GitStats without errors.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--7, FR--10, OE--IA1, SR--INT2, SR--INT3
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--DM--3
\vspace{0.4em}

\textbf{Input:} A Contributor or Super Admin edits a metric value for a library through the metric editing interface.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the updated metric value is stored successfully in the database and the AHP ranking is recalculated to reflect the new value.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the updated metric value is stored successfully in the database and the AHP ranking is recalculated to reflect the new value.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--7, FR--12, SR--INT4, SR--IM2
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--DM--4
\vspace{0.4em}

\textbf{Input:} An API request for repository analysis is forced to fail by temporarily reducing the request timeout during testing.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the system reports the analysis failure to the user while preserving previously stored metric data for the library.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the system displays a failure message in the interface while previously stored metric data remains unchanged.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} PR--RFT1, PR--RFT2, SR--INT5
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--DM--5
\vspace{0.4em}

\textbf{Input:} A user selects the export option to download the comparison table for a domain as an Excel file.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the system generates and downloads an Excel file containing all libraries in the selected domain along with their associated metrics and stored metric values.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the system generates and downloads an Excel file containing all libraries in the selected domain along with their associated metrics and stored metric values.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--14, SR--INT7, OE--PR4
\end{mdframed}

\subsection{Visualization and Reporting}

\hspace{2em}The following tests verify that the system correctly generates
visualizations for domain comparison and accurately represents stored
metric values for libraries.

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--VR--1
\vspace{0.4em}

\textbf{Input:} A user opens the visualization page for a domain containing at least three libraries, selects one or more metrics and libraries, and clicks the \textit{Visualize} button.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the system generates comparative graphs for the selected libraries and metrics on the visualization page.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the system generates comparative graphs for the selected libraries and metrics on the visualization page.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--13, FR--12, SR--VIS1, SR--IM1
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--VR--2
\vspace{0.4em}

\textbf{Input:} A user modifies the selected metrics or libraries on the visualization page and clicks the \textit{Visualize} button to regenerate the graphs.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the system updates the graphs to reflect the newly selected metrics or libraries.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the system updates the graphs to reflect the newly selected metrics or libraries.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--13, SR--VIS2, PR--SL1
\end{mdframed}


\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--VR--3
\vspace{0.4em}

\textbf{Input:} A user clicks the \textit{Download All} button on the visualization page after generating graphs.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the system generates and downloads the visualization plots as PNG image files.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the system generates and downloads the visualization plots as PNG image files.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--15, OE--PR4, SR--INT7
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--VR--4
\vspace{0.4em}

\textbf{Input:} A user resizes the browser window or opens the visualization page on different screen resolutions.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the graphs remain readable and the interface layout adjusts correctly without overlapping elements.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the graphs remain readable and the interface layout adjusts correctly without overlapping elements.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} LF--AR2, LF--SR2, UH--AR1
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--VR--5
\vspace{0.4em}

\textbf{Input:} A domain contains a library where one or more metric values are missing when the user generates visualization graphs.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the visualization is generated successfully and the system handles the missing metric value without runtime errors.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the visualization is generated successfully and the system handles the missing metric value without runtime errors.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} PR--RFT1, SR--INT5
\end{mdframed}

\begin{mdframed}[linewidth=0.5mm]
\setlength{\parindent}{0pt}
\textbf{Test Case Identifier:} T--VR--6
\vspace{0.4em}

\textbf{Input:} A user opens the Manage Metrics page for a domain.
\vspace{0.4em}

\textbf{Expected Output:} The expected result is that the system displays a list of all metrics associated with the domain, including their names and corresponding definitions or configuration details.
\vspace{0.4em}

\textbf{Actual Output:} The actual result is that the system displays a list of all metrics associated with the domain, including their names and corresponding definitions or configuration details.
\vspace{0.4em}

\textbf{Expected and Actual Output Match:} True
\vspace{0.4em}

\textbf{Relevant Functional Requirement(s):} FR--11, UH--LR2, LF--AR3
\end{mdframed}

\subsection{Features Currently in Progress}

\hspace{2em}Some functional requirements identified in the SRS are still under development, while others were revised after further discussion and feedback. These items are not yet fully implemented or were removed from the final project scope. Their current status is summarized below.

\begin{description}

\item[\textbf{SR--AC1:}] \textbf{Public Viewing and Restricted Editing}

This requirement is currently under development as part of the system's authorization implementation. The intended behaviour is to allow public users to view published domain data while restricting modification privileges to approved users only. Page-level and button-level authorization controls have been partially implemented and are still being refined.

\item[\textbf{FR--2:}] \textbf{User Self Sign-Up}

This requirement was originally intended to allow users to create their own accounts through a public sign-up page. During development, this design was reconsidered, and the system is being revised so that only a Super Admin can create new user accounts. As a result, self sign-up will not appear in the final implementation.

\item[\textbf{SR--AC6, SR--AU1, SR--IM1:}] \textbf{Unauthorized API Access Control}

Unauthorized API access control is currently under development. The intended behaviour is that attempts to perform restricted actions, such as deleting a domain without sufficient privileges, will return an HTTP 403 Forbidden response and generate an audit log entry. At present, restricted actions are hidden in the user interface, while API-level authorization checks are still being implemented and are not yet ready for formal testing.

Security requirements related to SQL injection prevention and secure credential storage are already satisfied through the use of the Django ORM, which avoids raw SQL queries, and environment variables for sensitive configuration data.

\item[\textbf{FR--4:}] \textbf{Password Reset via Email}

This feature is intended to allow users to reset their password through an email verification workflow. The expected behaviour is that a user who forgets their password receives a reset email, verifies their identity through a tokenized link, and sets a new password for future logins.

This functionality is currently under development and has not yet been fully implemented or tested.

\item[\textbf{FR--9:}] \textbf{Bulk Data Upload}

This requirement was originally intended to support bulk upload of domain data through an Excel template. Based on supervisor feedback, this functionality was removed from the project scope and will not be implemented. Therefore, no testing was performed for this requirement.

\textbf{Relevant Functional Requirement(s):} FR--9, SR--INT1, UH--EU2

\item[\textbf{FR--6:}] \textbf{Publish Domain for Public Access}

This feature is currently under development as part of the remaining authorization work. The intended behaviour is that a completed domain can be published and made visible to all users, with its data available for public viewing and download. This functionality will be completed together with the remaining access-control features.

\textbf{Relevant Functional Requirement(s):} FR--6, OE--PR3, FR--14

\end{description}
\section{Nonfunctional Requirements Evaluation}

\label{sec:nfr}

This section reports verification results for the system's nonfunctional
requirements (NFRs).  Each evaluation
includes explicit inputs and outputs, an expected-versus-actual comparison,
and traceability back to the relevant NFR identifiers.  Tables are used to
summarize results and to support reproducibility.

\subsection{Performance \& Scalability Experiments}
\label{sec:nfr-perfscalability}

This subsection reports Revision~0 results for the performance and
scalability experiment specified in the VnV Plan (\S4.2.1).  The experiment
measures response times for dashboard load, filtering, AHP recomputation, and
export, and summarizes median and 95th-percentile (p95) values.

\subsubsection{Test Case Summary (T--NF1: Performance and Scalability)}
\begin{table}[H]
  \centering
  \caption{T--NF1 performance experiment: test case summary (Rev0).}
  \label{tab:tnf1-summary}
  \begin{tabular}{@{}p{0.22\textwidth}p{0.73\textwidth}@{}}
    \toprule
    \textbf{Test Case ID} &
      T--NF1 (Performance and Scalability) \\
    \textbf{Traceability} &
      PR-SL1 (Speed and Latency Requirement). \\
    \textbf{Initial State} &
      System deployed and accessible; existing domains available with known
      library counts (2 and 10). \\
    \textbf{Input} &
      Record time to (1) load the dashboard and render the ranking graph,
      (2) apply a domain filter, (3) update category weights to trigger AHP
      recomputation, and (4) export visualizations. \\
    \textbf{Expected Output} &
      Median and p95 response times are recorded; response times remain within
      a few seconds for interactive use. \\
    \textbf{Actual Output} &
      Dashboard load and AHP recomputation completed within a few seconds.
      Domain filtering did not narrow results (no observable effect).  Export
      appeared instantaneous in repeated trials. \\
    \textbf{Expected vs.\ Actual Match} &
      Partial (latency acceptable for measured actions; filtering defect
      prevented filter timing; scaling evaluated at 2 and 10 libraries only). \\
    \bottomrule
  \end{tabular}
\end{table}

\subsubsection{Method (Rev0)}
Timings were collected manually using a stopwatch, measured from the moment
the action was initiated (click) to the moment the interface reached a stable
state (graph rendered or updated).  Due to manual timing, values include human
reaction time and should be treated as conservative upper bounds.  For small
sample sizes, p95 is reported conservatively as the maximum observed value.

\subsubsection{Results}
Table~\ref{tab:tnf1-results} summarizes the observed median and p95 response
times.

\begin{table}[H]
  \centering
  \caption{T--NF1 response time results (Rev0).}
  \label{tab:tnf1-results}
  \begin{tabular}{@{}p{0.44\textwidth}p{0.14\textwidth}p{0.14\textwidth}%
                  p{0.16\textwidth}@{}}
    \toprule
    \textbf{Action} & \textbf{Median (s)} & \textbf{p95 (s)} & \textbf{Notes} \\
    \midrule
    Dashboard load (2 libraries, n=8) &
      0.55 & 0.74 &
      Time to render ranking view. \\
    Dashboard load (10 libraries, n=10) &
      2.65 & 2.92 &
      Time to render ranking view. \\
    Recompute AHP (edit category weights, n=10) &
      3.61 & 3.90 &
      Time from save/apply to updated view. \\
    Apply domain filter &
      N/A & N/A &
      Filter input produced no narrowing of results. \\
    Export visualizations &
      $<0.5$ & $<0.5$ &
      Appeared instantaneous (below stopwatch resolution). \\
    \bottomrule
  \end{tabular}
\end{table}

\subsubsection{Analysis}
Across the measured actions, response times were within a few seconds, with
worst observed values below 4 seconds.  Dashboard load increased from a median
of 0.55 seconds (2 libraries) to a median of 2.65 seconds (10 libraries),
indicating higher latency as library count increases in the tested
configuration.  AHP recomputation completed in under 4 seconds in all trials,
which is acceptable for interactive use.

Domain filtering produced no observable narrowing of the domain list.  This is
treated as a functional defect and prevented measurement of filter latency in
Revision~0.

\subsubsection{Limitations and Next Steps}
Revision~0 results include only 2- and 10-library datasets and manual timing.
In the next revision, performance will be re-measured using the planned dataset
sizes (5, 10, 20, and 40 libraries) and automated timing collection where
possible.  The domain filtering defect will be addressed and re-tested to
capture filter latency.

\subsection{Reliability and Fault Tolerance}
\label{sec:nfr-reliability}

This subsection reports Revision~0 results for reliability and fault
tolerance.  The goal is to confirm the system remains stable, consistent, and
capable of recovery when services fail or operations are interrupted.

\subsubsection{Test Case Summary (T--NF2: Reliability and Fault Tolerance)}
\begin{table}[H]
  \centering
  \caption{T--NF2 reliability and fault tolerance: test case summary (Rev0).}
  \label{tab:tnf2-summary}
  \begin{tabular}{@{}p{0.22\textwidth}p{0.73\textwidth}@{}}
    \toprule
    \textbf{Test Case ID} &
      T--NF2 (Reliability and Fault Tolerance) \\
    \textbf{Traceability} &
      PR-RFT1--PR-RFT3, SR-INT5. \\
    \textbf{Initial State} &
      System deployed and accessible; at least one existing domain is loaded. \\
    \textbf{Input} &
      (1) Simulate service/API failure by forcing the client offline in the
      browser and attempt common read actions (switch view tabs and open the
      comparison tool).  (2) Interrupt a mid-update transaction by modifying
      category weights, clicking save, and toggling offline immediately after
      the save attempt.  (3) Restore connectivity and verify recovery and data
      integrity. \\
    \textbf{Expected Output} &
      The tool remains stable (no crash), displays a user-visible warning/error
      instead of failing silently, and recovers once services return.
      Interrupted updates rollback to the last valid state and do not leave
      partial/corrupt state. \\
    \textbf{Actual Output} &
      When offline, the interface remained responsive and did not crash.
      Domain metadata and results were not displayed (Details panel showed
      Name: N/A) and key actions produced no observable effect.  No user-visible
      warning or cached fallback results were observed.  After restoring
      connectivity (No throttling), the dashboard resumed normal operation and
      loaded domain details and rankings correctly.  In the interrupted-write
      test (save category weights then go offline), the system reverted to the
      pre-change configuration after recovery (the attempted change was not
      persisted), and no half-created/partial state was observed. \\
    \textbf{Expected vs.\ Actual Match} &
      Partial (stable, recoverable, and rollback-safe, but weak failure
      messaging and no offline fallback behavior). \\
    \bottomrule
  \end{tabular}
\end{table}

\subsubsection{Results}
\begin{table}[H]
  \centering
  \caption{Reliability experiment results (Rev0).}
  \label{tab:tnf2-results}
  \begin{tabular}{@{}p{0.44\textwidth}p{0.16\textwidth}p{0.32\textwidth}@{}}
    \toprule
    \textbf{Scenario} & \textbf{Result} & \textbf{Notes} \\
    \midrule
    Client forced offline (API failure proxy) &
      Partial &
      No crash; content unavailable (Name: N/A); actions no-op; no warning
      shown; no cached fallback observed. \\
    Recovery after reconnect &
      Pass &
      After returning online, domain details and rankings rendered normally. \\
    Interrupted mid-update transaction (save then offline) &
      Pass &
      After recovery the system reverted to the last valid state (changes not
      persisted); no partial state observed. \\
    Integrity after failure/recovery &
      Pass &
      No half-created/corrupt state observed in the UI after recovery. \\
    HTTP 429 (rate limiting) &
      Not tested &
      Not reproducible/observed in Rev0. \\
    Backup and restore (within one hour) &
      Pending &
      Requires DB-level procedure execution and timing. \\
    \bottomrule
  \end{tabular}
\end{table}

\subsubsection{Analysis}
The system remained stable during a simulated service outage (offline mode) and
successfully recovered once connectivity was restored.  The interrupted-write
test also indicates safe failure handling: the system returned to the last valid
configuration after recovery and did not leave partial or corrupt state.

However, the failure mode is not communicated clearly to the user: data becomes
unavailable and actions become no-ops without a warning message or fallback
behavior.  Improvements should include explicit error messaging, disabling
actions that require connectivity, and (if feasible) displaying cached last-known
results with an ``offline'' banner.  Save operations should also provide clear
success/failure feedback when the backend is unreachable.

\subsubsection{Limitations and Next Steps}
Revision~0 reliability evidence is based on manual fault injection (offline
mode) and a single interrupted-write scenario.  In the next revision,
explicit HTTP 429 scenarios will be exercised if rate limiting is enabled, and
a backup-and-restore procedure will be executed and timed to confirm recovery
within one hour.

\noindent \textbf{Conclusion:} Rev0 demonstrates stability and safe rollback
under outages, but highlights a gap in user-facing fault messaging and offline
fallback behavior.

\subsection{Usability}

\subsection{Performance}

\subsection{etc.}

\section{Comparison to Existing Implementation}


\section{Unit Testing}
The following unit tests concern behaviour-hiding modules that are implemented by the tool. Modules implemented by external libraries are assumed to be tested themselves and therefore don't need to be unit tested.
\subsection{Data Edit Module}
  \begin{enumerate}
    \item \texttt{test\_list\_libraries\_returns\_only\_domain\_libraries} \label{test-list-libraries-returns-only-domain-libraries}
      \\Initial State: Domain "D1" with 2 libraries, another domain "Other" with 1 library
      \\Input: GET request to \texttt{/api/libraries/by\_domain/\{domain\_ID\}/}
      \\Expected Output: Returns only libraries belonging to the specified domain
      \\Actual Output: Returned libraries "A" and "B" from domain "D1"
      \\Result: Pass
    \item \texttt{test\_create\_library\_requires\_domain} \label{test-create-library-requires-domain}
      \\Initial State: N/A
      \\Input: POST request to \texttt{/api/libraries/} with empty payload
      \\Expected Output: HTTP 400 Bad Request; domain is required
      \\Actual Output: Status 400, error indicates missing domain
      \\Result: Pass
    \item \texttt{test\_create\_library\_invalid\_domain} \label{test-create-library-invalid-domain}
      \\Initial State: N/A
      \\Input: POST request with invalid UUID for domain
      \\Expected Output: HTTP 400 Bad Request; invalid domain
      \\Actual Output: Status 400, error indicates domain field issue
      \\Result: Pass
    \item \texttt{test\_create\_library\_success\_sets\_pending\_and\_returns\_task\_id} \label{test-create-library-success-sets-pending-and-returns-task-id}
      \\Initial State: N/A
      \\Input: POST request with valid domain and library payload; enqueue analysis patched to return "task-123"
      \\Expected Output: Library created, analysis status pending, task ID returned
      \\Actual Output: Library created, \texttt{analysis\_status = PENDING}, \texttt{task\_id = "task-123"}
      \\Result: Pass
    \item \texttt{test\_create\_library\_enqueue\_raises\_marks\_failed\_and\_task\_id\_none} \label{test-create-library-enqueue-raises-marks-failed-and-task-id-none}
      \\Initial State: N/A
      \\Input: POST request with valid payload; enqueue analysis patched to raise RuntimeError("boom")
      \\Expected Output: Library created, analysis status FAILED, task ID is None
      \\Actual Output: Library \texttt{analysis\_status = FAILED}, \texttt{task\_id = None}, error message "boom"
      \\Result: Pass
    \item \texttt{test\_patch\_library\_success} \label{test-patch-library-success}
      \\Initial State: Library "OldName" exists under a domain
      \\Input: PATCH request to update \texttt{library\_name} to "NewName"
      \\Expected Output: Library updated successfully; name changed
      \\Actual Output: \texttt{library\_name = "NewName"} confirmed in response and database
      \\Result: Pass
    \item \texttt{test\_put\_library\_success} \label{test-put-library-success}
      \\Initial State: Library "Name1" exists
      \\Input: PUT request with new domain, name, URL, and programming language
      \\Expected Output: Library updated successfully with all new fields
      \\Actual Output: Fields updated as expected in response and database
      \\Result: Pass
    \item \texttt{test\_put\_library\_rejects\_non\_github\_url} \label{test-put-library-rejects-non-github-url}
      \\Initial State: Library exists with a GitHub URL
      \\Input: PUT request with a non-GitHub URL
      \\Expected Output: HTTP 400 Bad Request; URL field rejected
      \\Actual Output: Status 400; error returned for URL
      \\Result: Pass
    \item \texttt{test\_delete\_library\_not\_found} \label{test-delete-library-not-found}
      \\Initial State: N/A
      \\Input: DELETE request with non-existent library ID
      \\Expected Output: HTTP 404 Not Found
      \\Actual Output: Status 404
      \\Result: Pass
    \item \texttt{test\_delete\_library\_success} \label{test-delete-library-success}
      \\Initial State: Library "Temp" exists
      \\Input: DELETE request to remove the library
      \\Expected Output: HTTP 204 No Content; library deleted from database
      \\Actual Output: Status 204; library no longer exists in database
      \\Result: Pass
    \item \texttt{test\_library\_metric\_value\_update\_requires\_metrics\_dict} \label{test-library-metric-value-update-requires-metrics-dict}
      \\Initial State: Library "A" exists
      \\Input: POST request with invalid metrics payload (list instead of dict)
      \\Expected Output: HTTP 400 Bad Request; error indicates metrics must be dict
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_library\_metric\_value\_update\_creates\_value\_and\_evidence} \label{test-library-metric-value-update-creates-value-and-evidence}
      \\Initial State: Library "A" exists; metrics "Stars Count" and "Forks Count" exist
      \\Input: POST request updating metrics with values and evidence; includes unknown metric
      \\Expected Output: Values and evidence updated for known metrics; unknown metric ignored; HTTP 200
      \\Actual Output: Matches expected; database updated correctly
      \\Result: Pass
    \item \texttt{test\_metric\_value\_bulk\_update\_rejects\_non\_list} \label{test-metric-value-bulk-update-rejects-non-list}
      \\Initial State: N/A
      \\Input: POST request with non-list payload
      \\Expected Output: HTTP 400 Bad Request; error indicates expected a list
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_metric\_value\_bulk\_update\_empty\_list\_returns\_200} \label{test-metric-value-bulk-update-empty-list-returns-200}
      \\Initial State: N/A
      \\Input: POST request with empty list
      \\Expected Output: HTTP 200 OK; status indicates no data to update
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_metric\_value\_bulk\_update\_success} \label{test-metric-value-bulk-update-success}
      \\Initial State: Library "A" exists; metrics "Stars Count" and "Forks Count" exist
      \\Input: POST request with multiple update entries including empty and None values
      \\Expected Output: HTTP 200 OK; values updated accordingly; unknown library skipped
      \\Actual Output: Matches expected; stars updated to 99, forks set to None
      \\Result: Pass
    \item \texttt{test\_create\_library\_with\_description} \label{test-create-library-with-description}
      \\Initial State: Domain "D1" exists
      \\Input: POST request with valid payload including \texttt{description} field
      \\Expected Output: HTTP 201 Created; library description saved correctly
      \\Actual Output: Matches expected; description field populated
      \\Result: Pass

    \item \texttt{test\_create\_library\_description\_optional} \label{test-create-library-description-optional}
      \\Initial State: Domain "D1" exists
      \\Input: POST request with valid payload without \texttt{description} field
      \\Expected Output: HTTP 201 Created; library created with description = None
      \\Actual Output: Matches expected; description is null
      \\Result: Pass

    \item \texttt{test\_patch\_library\_description} \label{test-patch-library-description}
      \\Initial State: Library "Lib" exists with description "old description"
      \\Input: PATCH request to update \texttt{description} to "new description"
      \\Expected Output: HTTP 200 OK; description updated
      \\Actual Output: Matches expected; description changed
      \\Result: Pass

    \item \texttt{test\_put\_library\_includes\_description} \label{test-put-library-includes-description}
      \\Initial State: Library "Name1" exists
      \\Input: PUT request with new domain, name, description, URL, and programming language
      \\Expected Output: Library updated successfully with description field
      \\Actual Output: Fields updated as expected including description
      \\Result: Pass
  \end{enumerate}
\subsection{User Management Module}
  \begin{enumerate}
    \item \texttt{test\_list\_users\_superadmin} \label{test-list-users-superadmin}
    \\Input: Superadmin requests list of users
    \\Expected Output: HTTP 200 OK with serialized user list
    \\Actual Output: Response status is either 200 or 404 depending on endpoint availability
    \\Result: Pass
    \item \texttt{test\_list\_users\_admin\_forbidden} \label{test-list-users-admin-forbidden}
    \\Input: Admin user attempts to access user list endpoint
    \\Expected Output: HTTP 403 Forbidden
    \\Actual Output: Response status is either 403 or 404 depending on endpoint availability
    \\Result: Pass
    \item \texttt{test\_list\_users\_unauthenticated} \label{test-list-users-unauthenticated}
    \\Input: Unauthenticated request to list users endpoint
    \\Expected Output: HTTP 401 Unauthorized
    \\Actual Output: Response status is either 401 or 404 depending on endpoint availability
    \\Result: Pass
    \item \texttt{test\_update\_user\_basic\_fields} \label{test-update-user-basic-fields}
    \\Input: Superadmin updates another user's first and last name
    \\Expected Output: HTTP 200 OK with updated user fields
    \\Actual Output: Response status is either 200 or 404 depending on endpoint availability
    \\Result: Pass
    \item \texttt{test\_admin\_can\_update\_user\_but\_not\_role} \label{test-admin-update-no-role}
    \\Input: Admin attempts to update a user's first name and role
    \\Expected Output: First name updated but role change ignored
    \\Actual Output: Response 200 OK and role remains unchanged
    \\Result: Pass
    \item \texttt{test\_user\_can\_update\_own\_profile} \label{test-user-update-own-profile}
    \\Input: User updates their own first name
    \\Expected Output: HTTP 200 OK and first name updated
    \\Actual Output: Response 200 OK and first name modified
    \\Result: Pass
    \item \texttt{test\_admin\_cannot\_edit\_other\_user\_basic\_info} \label{test-admin-edit-other-user}
    \\Input: Admin attempts to change another user's first name
    \\Expected Output: Change is rejected and original value remains
    \\Actual Output: User's first name remains unchanged
    \\Result: Pass
    \item \texttt{test\_update\_user\_unauthenticated} \label{test-update-user-unauthenticated}
    \\Input: Unauthenticated user attempts to update user profile
    \\Expected Output: HTTP 401 Unauthorized
    \\Actual Output: Response status is either 401 or 404 depending on endpoint availability
    \\Result: Pass
    \item \texttt{test\_user\_cannot\_change\_others\_password} \label{test-change-password-forbidden}
    \\Input: Regular user attempts to change another user's password
    \\Expected Output: HTTP 403 Forbidden
    \\Actual Output: Response status 403 Forbidden
    \\Result: Pass
    \item \texttt{test\_superadmin\_can\_change\_others\_password} \label{test-superadmin-change-password}
    \\Input: Superadmin changes another user's password
    \\Expected Output: HTTP 200 OK and \texttt{set\_password()} called
    \\Actual Output: Password updated and response 200 OK
    \\Result: Pass
    \item \texttt{test\_owner\_can\_change\_own\_password} \label{test-owner-change-password}
    \\Input: User changes their own password with correct old password
    \\Expected Output: HTTP 200 OK and password updated
    \\Actual Output: \texttt{set\_password()} called and response 200 OK
    \\Result: Pass
  \end{enumerate}
\subsection{Automated Metrics Module}
  \begin{enumerate}
    \item \texttt{test\_extract\_repo\_info\_valid\_url} \label{test-extract-repo-info-valid-url}
      \\Input: Valid GitHub URL
      \\Expected Output: Repo owner and name parsed correctly
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_extract\_repo\_info\_strips\_git\_suffix} \label{test-extract-repo-info-strips-git-suffix}
      \\Input: URL ending with .git
      \\Expected Output: Repo owner and name parsed without .git
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_extract\_repo\_info\_invalid\_url\_raises} \label{test-extract-repo-info-invalid-url-raises}
      \\Input: Invalid GitHub URL
      \\Expected Output: Raises ValueError
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_parse\_last\_page\_from\_link\_returns\_page\_number} \label{test-parse-last-page-from-link-returns-page-number}
      \\Input: GitHub Link header with last page
      \\Expected Output: Returns last page number
      \\Actual Output: Matches expected (42)
      \\Result: Pass
    \item \texttt{test\_parse\_last\_page\_from\_link\_none\_or\_missing\_last\_returns\_none} \label{test-parse-last-page-from-link-none-or-missing-last-returns-none}
      \\Input: Empty, None, or Link header missing last
      \\Expected Output: Returns None
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_search\_count\_uses\_search\_endpoint\_and\_reads\_total\_count} \label{test-search-count-uses-search-endpoint-and-reads-total-count}
      \\Input: GitHub search query
      \\Expected Output: Calls /search/issues; returns total\_count
      \\Actual Output: Matches expected (123)
      \\Result: Pass
    \item \texttt{test\_get\_commits\_past\_five\_years\_returns\_0\_on\_409} \label{test-get-commits-past-five-years-returns-0-on-409}
      \\Input: GitHub returns 409
      \\Expected Output: Returns 0
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_get\_commits\_past\_five\_years\_uses\_last\_page\_if\_present} \label{test-get-commits-past-five-years-uses-last-page-if-present}
      \\Input: Link header includes last page
      \\Expected Output: Returns last page number
      \\Actual Output: Matches expected (77)
      \\Result: Pass
    \item \texttt{test\_get\_commits\_past\_five\_years\_falls\_back\_to\_json\_length} \label{test-get-commits-past-five-years-falls-back-to-json-length}
      \\Input: Link header missing
      \\Expected Output: Returns length of commits array
      \\Actual Output: Matches expected (1)
      \\Result: Pass
    \item \texttt{test\_get\_file\_type\_counts\_counts\_text\_and\_binary} \label{test-get-file-type-counts-counts-text-and-binary}
      \\Input: Repo tree with text and binary files
      \\Expected Output: Returns counts of text and binary files
      \\Actual Output: Matches expected (text=2, binary=2)
      \\Result: Pass
    \item \texttt{test\_get\_file\_type\_counts\_returns\_0\_0\_on\_non\_200} \label{test-get-file-type-counts-returns-0-0-on-non-200}
      \\Input: Response status not 200
      \\Expected Output: Returns (0,0)
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_get\_github\_api\_metrics\_happy\_path} \label{test-get-github-api-metrics-happy-path}
      \\Input: Repo with metrics available; patched internal methods
      \\Expected Output: Returns dictionary with all GitHub metrics
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_get\_github\_api\_metrics\_wraps\_request\_exception} \label{test-get-github-api-metrics-wraps-request-exception}
      \\Input: github\_get raises RequestException
      \\Expected Output: Raises Exception with "GitHub API Error"
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_repo\_filters\_to\_target\_int\_metrics} \label{test-analyze-repo-filters-to-target-int-metrics}
      \\Input: Metrics include int, None, string
      \\Expected Output: Only int metrics retained
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_run\_analysis\_and\_get\_data\_returns\_repo\_name\_and\_metric\_data} \label{test-run-analysis-and-get-data-returns-repo-name-and-metric-data}
      \\Input: Patched \_analyze\_repo returning metrics
      \\Expected Output: Returns repo\_name and metric\_data
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_repo\_task\_success\_updates\_metrics\_and\_marks\_success} \label{test-analyze-repo-task-success-updates-metrics-and-marks-success}
      \\Input: Valid library, metrics, RepoAnalyzer returns metrics
      \\Expected Output: Updates numeric metrics, marks library analysis as SUCCESS
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_repo\_task\_sets\_running\_status\_early} \label{test-analyze-repo-task-sets-running-status-early}
      \\Input: Library under analysis
      \\Expected Output: Analysis status is set to RUNNING before metrics updated
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_repo\_task\_exception\_marks\_failed\_and\_raises} \label{test-analyze-repo-task-exception-marks-failed-and-raises}
      \\Input: RepoAnalyzer raises RuntimeError
      \\Expected Output: Library marked as FAILED, analysis\_error recorded, exception propagated
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_repo\_gitstats\_task\_success\_sets\_report\_and\_metric} \label{test-analyze-repo-gitstats-task-success-sets-report-and-metric}
      \\Input: Valid library, RepoAnalyzer returns ok
      \\Expected Output: GitStats paths set, library gitstats\_status SUCCESS, metric created
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_repo\_gitstats\_task\_success\_without\_metric\_still\_succeeds} \label{test-analyze-repo-gitstats-task-success-without-metric-still-succeeds}
      \\Input: Valid library, no GitStats metric exists
      \\Expected Output: Task succeeds, library gitstats\_status SUCCESS, no metric created
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_repo\_gitstats\_task\_exception\_marks\_failed\_and\_raises} \label{test-analyze-repo-gitstats-task-exception-marks-failed-and-raises}
      \\Input: RepoAnalyzer.run\_gitstats\_only raises RuntimeError
      \\Expected Output: Library gitstats\_status FAILED, error recorded, exception propagated
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_library\_success\_202} \label{test-analyze-library-success-202}
      \\Initial State: Library "A" exists
      \\Input: POST request to analyze library; enqueue patched to return task IDs
      \\Expected Output: HTTP 202 Accepted; analysis queued with task IDs
      \\Actual Output: Status 202; response includes analysis\_task\_id "t1" and gitstats\_task\_id "g1"
      \\Result: Pass
    \item \texttt{test\_analyze\_library\_enqueue\_returns\_none\_400} \label{test-analyze-library-enqueue-returns-none-400}
      \\Initial State: Library "A" has \texttt{analysis\_error = "bad"}
      \\Input: POST request to analyze library; enqueue patched to return None
      \\Expected Output: HTTP 400 Bad Request; error returned
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_library\_enqueue\_raises\_500\_and\_marks\_failed} \label{test-analyze-library-enqueue-raises-500-and-marks-failed}
      \\Initial State: Library "A" exists
      \\Input: POST request; enqueue patched to raise RuntimeError("boom")
      \\Expected Output: HTTP 500 Internal Server Error; library analysis status FAILED and error recorded
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_analyze\_domain\_libraries\_mixed\_results} \label{test-analyze-domain-libraries-mixed-results}
      \\Initial State: Domain with libraries "A" and "B"
      \\Input: POST request to analyze all domain libraries; enqueue patched to succeed for "A" and fail for "B"
      \\Expected Output: HTTP 202 Accepted; queued and failed lists populated appropriately
      \\Actual Output: Matches expected; queued includes "A", failed includes "B"
      \\Result: Pass
    \item \texttt{test\_analyze\_domain\_libraries\_exception\_marks\_failed} \label{test-analyze-domain-libraries-exception-marks-failed}
      \\Initial State: Domain with libraries "A" and "B"
      \\Input: POST request; enqueue raises exception for "A"
      \\Expected Output: Library "A" marked FAILED; "B" queued; response HTTP 202
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_library\_analysis\_missing\_url} \label{test-library-analysis-missing-url}
      \\Input: Library with no URL
      \\Expected Output: Task not queued, library marked as FAILED, error set
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_library\_analysis\_with\_url\_queues\_both\_tasks\_and\_sets\_ids} \label{test-library-analysis-with-url-queues-both-tasks-and-sets-ids}
      \\Input: Library with valid URL
      \\Expected Output: Both Celery tasks queued, library task IDs recorded, analysis and gitstats statuses set to PENDING
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_validate\_metric\_value\_accepts\_bounded\_int\_in\_range} \label{test-validate-metric-value-accepts-bounded-int-in-range}
      \\Initial State: Metric with bounded int rule (min=1, max=10)
      \\Input: Value "7"
      \\Expected Output: Validation passes; value = 7
      \\Actual Output: Matches expected
      \\Result: Pass

    \item \texttt{test\_validate\_metric\_value\_rejects\_bounded\_int\_below\_min} \label{test-validate-metric-value-rejects-bounded-int-below-min}
      \\Initial State: Metric with bounded int rule (min=1)
      \\Input: Value "0"
      \\Expected Output: Validation fails; error message about min value
      \\Actual Output: Matches expected
      \\Result: Pass

    \item \texttt{test\_validate\_metric\_value\_rejects\_bounded\_int\_above\_max} \label{test-validate-metric-value-rejects-bounded-int-above-max}
      \\Initial State: Metric with bounded int rule (max=10)
      \\Input: Value "11"
      \\Expected Output: Validation fails; error message about max value
      \\Actual Output: Matches expected
      \\Result: Pass

    \item \texttt{test\_validate\_metric\_value\_accepts\_free\_int} \label{test-validate-metric-value-accepts-free-int}
      \\Initial State: Metric with free int rule (no bounds)
      \\Input: Value "2120234324"
      \\Expected Output: Validation passes; value = 2120234324
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_metric\_update\_weight\_view\_updates\_weight} \label{test-metric-update-weight-view-updates-weight}
      \\Initial State: Metric exists with weight=1.0
      \\Input: PATCH request to \texttt{/api/metrics/\{metric\_ID\}/update-weight/} with weight=4.25
      \\Expected Output: HTTP 200 OK; weight updated to 4.25
      \\Actual Output: Matches expected
      \\Result: Pass

    \item \texttt{test\_metric\_update\_weight\_view\_returns\_400\_when\_weight\_missing} \label{test-metric-update-weight-view-returns-400-when-weight-missing}
      \\Initial State: Metric exists
      \\Input: PATCH request to \texttt{/api/metrics/\{metric\_ID\}/update-weight/} with empty payload
      \\Expected Output: HTTP 400 Bad Request; error indicates weight field is required
      \\Actual Output: Matches expected
      \\Result: Pass

    \item \texttt{test\_metric\_list\_flat\_view\_returns\_only\_id\_and\_name} \label{test-metric-list-flat-view-returns-only-id-and-name}
      \\Initial State: Multiple metrics exist with various fields
      \\Input: GET request to \texttt{/api/metrics/flat/}
      \\Expected Output: HTTP 200 OK; each returned object contains only \texttt{metric\_ID} and \texttt{metric\_name}
      \\Actual Output: Matches expected
      \\Result: Pass
  \end{enumerate}
\subsection{Domains Page Module}
  \begin{enumerate}
    \item \texttt{test\_create\_domain\_success} \label{test-create-domain-success}
      \\Initial State: Create user and fixture of API client
      \\Input: Create payload containing domain name, description, and \texttt{creator\_ids} with the creator and call POST
      \\Expected Output: Response returns status 201 for created, and querying for the domain object contains the same as in the payload
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_create\_domain\_missing\_domain\_name} \label{test-create-domain-missing-domain-name}
      \\Initial State: Create fixture of API client
      \\Input: Create payload with only description and call POST
      \\Expected Output: Response returns 400 bad request and informs of missing field
      \\Actual Output: Matches expected, data returns dictionary with \texttt{domain\_name} and value of "This field is required"
      \\Result: Pass
    \item \texttt{test\_create\_domain\_missing\_description} \label{test-create-domain-missing-description}
      \\Initial State: Create fixture of API client
      \\Input: Create payload with only domain name and call POST
      \\Response returns 400 bad request and informs of missing field
      \\Actual Output: Matches expected, data returns dictionary with "description" and value of "Description field is required"
      \\Result: Pass
    \item \texttt{test\_list\_domains} \label{test-list-domains}
      \\Initial State: Create fixture of API client and create two domain objects
      \\Input: Calling GET for domain
      \\Expected Output: Response 200 OK with list of domains matching the created domains
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_update\_domain\_sets\_creators} \label{test-update-domain-sets-creators}
      \\Initial State: Create domain object with only \texttt{domain\_name} and description and fixture of API client
      \\Input: Create two users and add them to a payload with updated domain name and description. Then call POST with the domain ID
      \\Expected Output: Response 200, domain should contain the new information and be linked to the two users
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_delete\_domain} \label{test-delete-domain}
      \\Initial State: Create fixture of API client and create a domain object
      \\Input: Call DELETE with the domain ID
      \\Expected Output: Querying for the domain ID returns None
      \\Actual Output: Matches Expected
      \\Result: Pass
  \end{enumerate}
\subsection{Comparison Module}
  \begin{enumerate}
    \item \texttt{test\_ahp\_calculations\_success} \label{test-ahp-calculations-success}
      \\Initial State: Domain "AHP Test Domain" with category weight {"Performance": 1.0}; Metric in category "Performance"; Library "TestLib"
      \\Input: GET request to \texttt{/api/ahp-calculations/\{domain\_ID\}/} with mocked rules.json and categories.json
      \\Expected Output: HTTP 200 OK; response includes domain name, global ranking containing "TestLib"; library's ahp\_results saved with positive overall score
      \\Actual Output: library.ahp\_results["overall\_score"] is greater than 0
      \\Result: Pass
    \item \texttt{test\_ahp\_calculations\_not\_found} \label{test-ahp-calculations-not-found}
      \\Initial State: N/A
      \\Input: GET request to \texttt{/api/ahp-calculations/999/} (non-existent domain ID)
      \\Expected Output: HTTP 404 Not Found
      \\Actual Output: Status 404 returned
      \\Result: Pass
    \item \texttt{test\_ahp\_calculations\_with\_weighted\_categories} \label{test-ahp-calculations-with-weighted-categories}
      \\Initial State: Domain "Weighted Domain" with category weights {"Performance": 0.8, "Security": 0.2}; Metrics for both categories; Library "SecureLib"
      \\Input: GET request to \texttt{/api/ahp-calculations/\{domain\_ID\}/} with mocked rules.json and categories.json
      \\Expected Output: HTTP 200 OK; response includes both "Performance" and "Security" in category\_details; library's ahp\_results include scores for both categories
      \\Actual Output: library.ahp\_results["category\_scores"] contains both categories
      \\Result: Pass
    \item \texttt{test\_ahp\_calculations\_basic} \label{test-ahp-calculations-basic}
      \\Initial State: Domain with libraries "A" and "B"; metric "Score" exists; rules.json and categories.json mocked
      \\Input: GET request to AHP calculation endpoint
      \\Expected Output: HTTP 200 OK; global ranking includes both libraries; ahp\_results populated for both
      \\Actual Output: Matches expected; overall\_score and category\_scores present
      \\Result: Pass
    \item \texttt{test\_domain\_comparison\_returns\_metrics\_and\_rows\_with\_values\_and\_evidence} \label{test-domain-comparison-returns-metrics-and-rows-with-values-and-evidence}
      \\Initial State: Domain with libraries "A" and "B"; metrics "Stars Count" and "Forks Count"; metric values assigned
      \\Input: GET request to domain comparison endpoint
      \\Expected Output: HTTP 200 OK; metrics and library rows include values and evidence; gitstats\_report\_url populated
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_ahp\_filters\_to\_only\_paper\_qualities} \label{test-ahp-filters-to-only-paper-qualities}
      \\Initial State: Domain with categories including AHP qualities (Installability, Maintainability) and non-AHP qualities (Popularity, Raw Metrics)
      \\Input: GET request to AHP calculation endpoint
      \\Expected Output: Only the 9 PAPER\_QUALITIES appear in category\_details; non-AHP qualities are filtered out
      \\Actual Output: Matches expected; category\_details contains only AHP qualities
      \\Result: Pass
  \end{enumerate}
\subsection{Visualization Module}
\begin{enumerate}
    \item \texttt{test\_library\_raw\_values\_appear} \label{test-library-raw-values-appear}
    \\Initial State: With a new domain, create library "A" and library "B", and input "123" and "456" for the Commit Count metric for each library respectively.
    \\Input: Selecting the two libraries and associated commit count metric and press visualize.
    \\Expected Output: Bar graph of Commit Count appears with library "A" and "B" as a bar graph, with the value of the bar being "123" and "456" respectively.
    \\Actual Output: Matches expected
    \\Result: Pass
    \item \texttt{test\_missing\_metric\_values} \label{test-missing-metric-values}
    \\Initial State: With a new domain, create library "A" and library "B", and input "123" for "A" for the Commit Count metric.
    \\Input: Selecting the two libraries and associated commit count metric and press visualize.
    \\Expected Output: No graph appears, error message appears informing user that an issue occurred.
    \\Actual Output: No graph appears, error message stating "Invalid metrics selected" appears above the visualization button.
    \\Result: Pass
    \item \texttt{test\_error\_shown\_when\_less\_then\_two\_libraries\_are\_selected} \label{test-error-shown-when-less-then-two-libraries-are-selected}
    \\Initial State: With a new domain, create library "A" and library "B", and input "123" for "A" for the Commit Count metric.
    \\Input: Select "A" and Commit Count metric and press visualize.
    \\Expected Output: No graph appears, error message appears informing user that an issue occurred.
    \\Actual Output: No graph appears, error message stating "At least two libraries must be selected" appears above the visualization button.
    \\Result: Pass
    \item \texttt{test\_only\_display\_non\-text\_metrics} \label{test-only-display-non-text-metrics}
    \\Initial State: With a new domain, create a new metric called Institutions and set the type to string. Create library "A" and library "B" and metric values "McMaster" and "UofT" for the metric respectively.
    \\Input: Select "A" and "B".
    \\Expected Output: The Institutions metric should not appear in the metrics tab.
    \\Actual Output: Matches expected.
    \\Result: Pass
    \item \texttt{test\_download\_visualizations} \label{test-download-visualizations}
    \\Initial State: With a new domain, create library "A" and library "B", and input "123" and "456" for the Commit Count metric for each library respectively.
    \\Input: Select both libraries and the Commit Count metric and press Visualize, then select Download All.
    \\Expected Output: A zip folder with the visualization is downloaded on the user's computer. Unzipping and opening the folder we can see the same visualized graph.
    \\Actual Output: Matches expected.
    \\Result: Pass
\end{enumerate}
\subsection{Database Persistence Module}
  \begin{enumerate}
    \item \texttt{test\_domain\_str\_returns\_name} \label{test-domain-str-returns-name}
      \\Initial State: N/A
      \\Input: Directly creating a new domain object with \texttt{domain\_name} "Alpha" and description "desc"
      \\Expected Output: Calling newly created object returns the domain name "Alpha"
      \\Actual Output: Returned "Alpha"
      \\Result: Pass
    \item \texttt{test\_get\_domain\_ID\_returns\_string\_uuid} \label{test-get-domain-ID-returns-string-uuid}
      \\Initial State: N/A
      \\Input: Directly creating a new domain object with \texttt{domain\_name} "Beta" and description "desc"
      \\Expected Output: Calling \texttt{get\_domain\_ID()} on new domain returns the UUID
      \\Actual Output: Method matches \texttt{domain\_id} parameter and is instance of string
      \\Result: Pass
    \item \texttt{test\_defaults\_and\_blank\_fields}\label{test-defaults-and-blank-fields}
      \\Initial State: N/A
      \\Input: Directly creating a new domain object with \texttt{domain\_name} "Gamma"
      \\Expected Output: Initializes domain object with default fields \texttt{{published: False, paper\_name: None, paper\_url: "", category\_weights: {}}}
      \\Actual Output: Output matches expected
      \\Result: Pass
    \item \texttt{test\_unique\_domain\_name\_constraint} \label{test-unique-domain-name-constraint}
      \\Initial State: Domain object with \texttt{domain\_name} "Delta" and description "one"
      \\Input: Directly creating a new domain object with \texttt{domain\_name} "Delta" and description "two"
      \\Expected Output: Throws integrity error due to duplicate domain names
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_creators\_many\_to\_many\_assignment} \label{test-creators-many-to-many-assignment}
      \\Initial State: Create two users with admin role
      \\Input: Create two domain objects with separate names, add both creators to each domain.
      \\Expected Output: Filtering in each domain's creators by the id of the creator, both creators should exist
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_library\_str\_returns\_name} \label{test-library-str-returns-name}
      \\Initial State: N/A
      \\Input: Directly creating a new library object with \texttt{library\_name} "LibA" under a domain "D1"
      \\Expected Output: Calling \texttt{str()} on the library object returns "LibA"
      \\Actual Output: Returned "LibA"
      \\Result: Pass
    \item \texttt{test\_get\_library\_id\_returns\_string\_uuid} \label{test-get-library-id-returns-string-uuid}
      \\Initial State: N/A
      \\Input: Directly creating a new library object "LibB" under a domain "D2"
      \\Expected Output: Calling \texttt{get\_library\_id()} returns the library's UUID as a string
      \\Actual Output: Method returns a string that matches the library\_ID
      \\Result: Pass
    \item \texttt{test\_defaults\_and\_blank\_fields} \label{test-defaults-and-blank-fields}
      \\Initial State: N/A
      \\Input: Directly creating a new library object "LibC" under a domain "D3"
      \\Expected Output: Default fields initialized: \texttt{ahp\_results={}}, optional fields None, statuses set to pending, timestamps set
      \\Actual Output: Matches expected default values
      \\Result: Pass
    \item \texttt{test\_unique\_library\_name\_per\_domain\_constraint} \label{test-unique-library-name-per-domain-constraint}
      \\Initial State: Library object "SameName" exists under domain "D4"
      \\Input: Attempt to create another library with \texttt{library\_name="SameName"} in the same domain
      \\Expected Output: Raises \texttt{IntegrityError} due to duplicate name in the same domain
      \\Actual Output: IntegrityError raised
      \\Result: Pass
    \item \texttt{test\_same\_library\_name\_allowed\_in\_different\_domains} \label{test-same-library-name-allowed-in-different-domains}
      \\Initial State: Two different domains "D5A" and "D5B"
      \\Input: Create libraries with the same name "SharedName" in both domains
      \\Expected Output: Each domain can have the same library name independently
      \\Actual Output: Both libraries exist in their respective domains
      \\Result: Pass
    \item \texttt{test\_unique\_url\_per\_domain\_constraint} \label{test-unique-url-per-domain-constraint}
      \\Initial State: Library object with URL "https://github.com/x/y" exists in domain "D6"
      \\Input: Attempt to create another library with the same URL in the same domain
      \\Expected Output: Raises \texttt{IntegrityError} due to duplicate URL
      \\Actual Output: IntegrityError raised
      \\Result: Pass
    \item \texttt{test\_same\_url\_allowed\_in\_different\_domains} \label{test-same-url-allowed-in-different-domains}
      \\Initial State: Two different domains "D7A" and "D7B"
      \\Input: Create libraries with the same URL "https://github.com/x/y" in both domains
      \\Expected Output: URL uniqueness is enforced per domain only
      \\Actual Output: Both libraries exist in their respective domains
      \\Result: Pass
    \item \texttt{test\_null\_url\_does\_not\_break\_basic\_creation} \label{test-null-url-does-not-break-basic-creation}
      \\Initial State: N/A
      \\Input: Create a library with \texttt{url=None} under domain "D8"
      \\Expected Output: Library created successfully with \texttt{url=None}
      \\Actual Output: Library created, \texttt{url} is None
      \\Result: Pass
    \item \texttt{test\_library\_metric\_value\_str\_format} \label{test-library-metric-value-str-format}
      \\Initial State: Library "RepoA" and Metric "Stars Count" exist
      \\Input: Create a LibraryMetricValue with \texttt{value=\{"count": 10\}}
      \\Expected Output: \texttt{str(lmv)} returns "RepoA - Stars Count: \{'count': 10\}"
      \\Actual Output: Returned string matches expected
      \\Result: Pass
    \item \texttt{test\_value\_id\_is\_uuid} \label{test-value-id-is-uuid}
      \\Initial State: Library "RepoA" and Metric exist
      \\Input: Create a LibraryMetricValue with numeric value 5
      \\Expected Output: \texttt{value\_ID} is an instance of UUID
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_value\_can\_be\_null} \label{test-value-can-be-null}
      \\Initial State: Library "RepoA" and Metric exist
      \\Input: Create a LibraryMetricValue with \texttt{value=None}
      \\Expected Output: Value remains None; string representation shows "None"
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_optional\_fields\_defaults} \label{test-optional-fields-defaults}
      \\Initial State: Library and Metric exist
      \\Input: Create a LibraryMetricValue without providing optional fields
      \\Expected Output: \texttt{value, evidence, collected\_by = None}; \texttt{last\_modified} is set
      \\Actual Output: Matches expected defaults
      \\Result: Pass
    \item \texttt{test\_last\_modified\_updates\_on\_save} \label{test-last-modified-updates-on-save}
      \\Initial State: LibraryMetricValue created with value 1
      \\Input: Modify value to 2 and save
      \\Expected Output: \texttt{last\_modified} timestamp updated
      \\Actual Output: \texttt{last\_modified} >= previous timestamp
      \\Result: Pass
    \item \texttt{test\_cascade\_delete\_when\_library\_deleted} \label{test-cascade-delete-when-library-deleted}
      \\Initial State: Library "ToDelete" exists with one associated LibraryMetricValue
      \\Input: Delete the library
      \\Expected Output: Associated LibraryMetricValue is deleted
      \\Actual Output: LibraryMetricValue no longer exists
      \\Result: Pass
    \item \texttt{test\_cascade\_delete\_when\_metric\_deleted} \label{test-cascade-delete-when-metric-deleted}
      \\Initial State: Metric "Forks Count" exists with one LibraryMetricValue
      \\Input: Delete the metric
      \\Expected Output: Associated LibraryMetricValue is deleted
      \\Actual Output: LibraryMetricValue no longer exists
      \\Result: Pass
    \item \texttt{test\_str\_returns\_email} \label{test-str-returns-email}
      \\Input: User with email ``alice@example.com``
      \\Expected Output: \texttt(str(user)) returns the email
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_get\_full\_name\_returns\_none\_if\_missing\_parts} \label{test-get-full-name-none}
      \\Input: User without first\_name and last\_name
      \\Expected Output: \texttt(get\_full\_name()) returns None
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_get\_full\_name\_concatenates\_first\_and\_last} \label{test-get-full-name-concat}
      \\Input: User with first\_name ``Carol`` and last\_name ``Danvers``
      \\Expected Output: \texttt(get\_full\_name()) returns ``Carol Danvers``
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_role\_default\_is\_user} \label{test-role-default-user}
      \\Input: User created without specifying role
      \\Expected Output: ``role`` defaults to ``user``
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_email\_unique\_constraint} \label{test-email-unique-constraint}
      \\Input: Attempt to create two users with the same email
      \\Expected Output: Raises IntegrityError
      \\Actual Output: Matches expected
      \\Result: Pass
    \item \texttt{test\_library\_description\_field\_can\_be\_set} \label{test-library-description-field-can-be-set}
      \\Initial State: Domain "D1" exists
      \\Input: Create library with description field
      \\Expected Output: Library created with description saved correctly
      \\Actual Output: Matches expected; description field populated
      \\Result: Pass

    \item \texttt{test\_library\_description\_field\_optional} \label{test-library-description-field-optional}
      \\Initial State: Domain "D1" exists
      \\Input: Create library without description field
      \\Expected Output: Library created with description = None
      \\Actual Output: Matches expected; description is null
      \\Result: Pass

    \item \texttt{test\_library\_description\_can\_be\_updated} \label{test-library-description-can-be-updated}
      \\Initial State: Library exists with description "old description"
      \\Input: Update description to "new description" via PATCH request
      \\Expected Output: HTTP 200 OK; description updated
      \\Actual Output: Matches expected; description changed
      \\Result: Pass
  \end{enumerate}

\section{Changes Due to Testing}

\subsection{AHP Methodology Alignment}
Following the feedback from the Rev 0 meeting and further analysis of the Lattice Boltzmann Method (LBM) research paper, we identified several discrepancies between our initial implementation and the established research methodology.

\begin{itemize}
  \item \textbf{Pairwise Comparison Formula:} Our previous implementation used a symmetric comparison approach. We updated the AHP calculation to use the paper's exact formula: 
  \[
  A_{jk} = 
  \begin{cases} 
  \min(9, x_{sub} - y_{sub} + 1) & \text{if } x_{sub} \geq y_{sub} \\
  1 / \min(9, y_{sub} - x_{sub} + 1) & \text{if } x_{sub} < y_{sub}
  \end{cases}
  \]
  This ensures the pairwise matrix maintains the required reciprocal property ($A_{jk} = 1 / A_{kj}$).

  \item \textbf{Criteria Selection:} Previously, all categories from \texttt{categories.json} were included in the overall AHP ranking. Following the paper's methodology, we now filter to only the 9 specific qualities:
  \begin{itemize}
    \item Installability
    \item Correctness and Verifiability
    \item Surface Reliability
    \item Surface Robustness
    \item Surface Usability
    \item Maintainability
    \item Reusability
    \item Surface Understandability
    \item Visibility/Transparency
  \end{itemize}
  Non-AHP qualities (such as Popularity, Activity, and Raw Metrics) are now properly filtered out and do not affect the final rankings.

  \item \textbf{Criterion Weighting and Consistency Ratio:} To align with the formal AHP framework, we transitioned to a Pairwise Comparison Matrix for criterion weighting. Users now compare the relative importance of categories (e.g., Usability vs. Reliability) using the Saaty 1--9 scale. The system then mathematically derives the global weights and validates the results via a Consistency Ratio (CR) check, displaying the CR percentage to users. The interface requires CR $<$ 0.1 (10\%) before allowing the weights to be saved, ensuring the data is scientifically sound and preventing inconsistent judgments (e.g., A > B, B > C, but C > A).
\end{itemize}

\subsection{Data Integrity and Input Validation}
To reduce user error, we refined the data entry process.

\begin{itemize}
  \item \textbf{Context-Aware Inputs:} We replaced open-ended text fields with context-aware inputs. The system now provides dropdown menus for Booleans and Ranges based on the \texttt{rules.json} templates, preventing invalid data types from corrupting the AHP calculations.
  
  \item \textbf{Bounded Integer Validation:} For metrics with bounded integer rules (e.g., scale 1-10), the system now enforces min/max validation. Values outside the allowed range are rejected with descriptive error messages.
  
  \item \textbf{Scoring Dictionary Support:} Metrics can now define a \texttt{scoring\_dict} mapping allowed values to scores (e.g., \{"MIT": 5, "Apache-2.0": 4\}), ensuring consistent scoring across libraries.
\end{itemize}

\subsection{Visualization and Data Density}
We addressed the limitations regarding how library rankings were displayed to improve transparency and usability.

\begin{itemize}
  \item \textbf{Graph Scalability:} Previously, the dashboard was limited to the top 10 libraries to avoid overcrowding. To provide a comprehensive view of the domain, we have redesigned the visualization format to clearly accommodate and display all libraries simultaneously.
  
  \item \textbf{Per-Quality AHP Visualization:} Users can now view the AHP calculations for individual qualities beyond just the overall ranking. A filter panel allows users to select which specific quality rankings to display (e.g., Installability only, Maintainability only), providing deeper insight into how each library performs across different dimensions.
  
  \item \textbf{Ranking Table with Sorting:} Based on user recommendations, we have introduced a Ranking Table to complement the graphical data. The table displays all libraries with their overall scores and scores for each individual quality. Users can reorder the table by clicking on any column header, allowing them to sort by overall ranking, Installability, Maintainability, or any other quality to quickly identify top performers in specific categories.
\end{itemize}

\subsection{User Interface Improvements for Metric Editing}
Based on user feedback regarding the difficulty of scrolling through large tables with many metrics, we redesigned the metric editing interface.

\begin{itemize}
  \item \textbf{Modular Design:} The editing page was restructured to use a modular, tab-based layout. Instead of displaying all metrics in a single scrollable table, metrics are now organized by category. Users can navigate between categories using tabs, significantly reducing scrolling and improving the editing experience.
  
  \item \textbf{Improved Navigation:} Each category tab displays only the metrics relevant to that category, making it easier for users to find and edit specific values without losing context.
\end{itemize}

\subsection{Test Results Summary}
Unit testing was conducted across all modules to validate the changes. Key results include:

\begin{itemize}
  \item \textbf{Data Edit Module:} 19 tests passed, validating library CRUD operations, metric value updates, and description field handling.
  
  \item \textbf{User Management Module:} 11 tests passed, confirming role-based access control and password management.
  
  \item \textbf{Automated Metrics Module:} 35 tests passed, including validation of bounded integers, free integers, date/time handling, and metric weight updates.
  
  \item \textbf{Domains Page Module:} 6 tests passed, covering domain creation, updates, and deletion.
  
  \item \textbf{Comparison Module:} 6 tests passed, including AHP filtering to only paper qualities, weighted category calculations, and domain comparison endpoints.
  
  \item \textbf{Visualization Module:} 5 tests passed, verifying graph generation, error handling for missing data, and download functionality.
  
  \item \textbf{Database Persistence Module:} 28 tests passed, confirming model constraints, cascading deletes, and default field initialization.
\end{itemize}

\textit{Note: All 110 unit tests passed. No critical issues were identified; the core logic remains stable.}

\section{Automated Testing}

Pytest and the \texttt{pytest-django} ecosystem serve as the foundation for our automated testing suite, which offers a high-performance, adaptable framework for verifying environment setups and application logic. To ensure that model-level constraints are carefully enforced before code reaches production, we use specialized decorators like \texttt{@pytest.mark.django\_db} to safely communicate with a temporary test database. We can swiftly find and fix errors in our fundamental business logic, such the concatenation rules for user profiles, by utilizing Pytest's sophisticated assertion introspection.

Using Django's \texttt{SimpleTestCase} and the \texttt{unittest.mock} module, we developed a strong configuration testing method in addition to standard data validation. This enables us to test that our settings dynamically swap between SQLite and MySQL engines as planned by programmatically simulating various deployment scenarios (e.g., Local vs. Production). We make sure the application stays stable and properly configured across different infrastructure states without having to manually review environment files by simulating environment variables and altering settings within our tests.
\section{Trace to Requirements}
Table~\ref{tab:trace} presents the traceability between the
system test cases and the requirements defined in the Software Requirements
Specification (SRS). The table indicates which test cases provide verification
evidence for each requirement implemented in the system.
		
\begin{table}[H]
\centering
\caption{Traceability Between Requirements and System Test Cases}
\label{tab:trace}
\resizebox{\textwidth}{!}{
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Requirement & T-AC-1 & T-AC-2 & T-AC-3 & T-AC-4 & T-AC-5 & T-DM-1 & T-DM-2 & T-DM-3 & T-DM-4 & T-DM-5 & T-VR-1 & T-VR-2 & T-VR-3 & T-VR-4 & T-VR-5 & T-VR-6 \\ \hline

FR2  & X &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
FR3  &  & X & X &  &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
FR4  &  &  &  & X &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
FR5  &  &  &  &  &  & X &  &  &  &  &  &  &  &  &  &  \\ \hline
FR7  &  &  &  &  &  &  & X & X &  &  &  &  &  &  &  &  \\ \hline
FR10 &  &  &  &  &  &  & X &  &  &  &  &  &  &  &  &  \\ \hline
FR11 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & X \\ \hline
FR12 &  &  &  &  &  &  &  & X &  &  & X &  &  &  &  &  \\ \hline
FR13 &  &  &  &  &  &  &  &  &  &  & X & X &  &  &  &  \\ \hline
FR14 &  &  &  &  &  &  &  &  &  & X &  &  &  &  &  &  \\ \hline
FR15 &  &  &  &  &  &  &  &  &  &  &  &  & X &  &  &  \\ \hline

SR-AC4 &  &  &  &  & X &  &  &  &  &  &  &  &  &  &  &  \\ \hline
SR-AC5 & X & X & X & X &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline

SR-VIS1 &  &  &  &  &  &  &  &  &  &  & X &  &  &  &  &  \\ \hline
SR-VIS2 &  &  &  &  &  &  &  &  &  &  &  & X &  &  &  &  \\ \hline

PR-RFT1 &  &  &  &  &  &  &  &  & X &  &  &  &  &  & X &  \\ \hline
SR-INT5 &  &  &  &  &  &  &  &  & X &  &  &  &  &  & X &  \\ \hline

LF-AR2 &  &  &  &  &  &  &  &  &  &  &  &  &  & X &  &  \\ \hline
LF-AR3 &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & X \\ \hline
LF-SR2 &  &  &  &  &  &  &  &  &  &  &  &  &  & X &  &  \\ \hline

UH-AR1 &  &  &  &  &  &  &  &  &  &  &  &  &  & X &  &  \\ \hline

OE-PR4 &  &  &  &  &  &  &  &  &  & X &  &  & X &  &  &  \\ \hline

\end{tabular}
}
\end{table}

The tests listed in this report were primarily designed to verify
functional requirements. However, some of these tests also provide
evidence related to certain non-functional requirements, which is why
those requirements appear in the traceability matrix. Requirements that
were still under development or removed from the final project scope are
not included in the table and are discussed earlier in the
\textit{Features Currently in Progress} subsection of the
\textit{Functional Requirements Evaluation} section.

\section{Trace to Requirements (Nonfunctional)}
\label{sec:trace-nfr}

Table~\ref{tab:trace-nfr} summarizes traceability between nonfunctional
requirements (NFR-related requirement IDs from the SRS) and the nonfunctional
test cases (T--NF1 through T--NF6) defined in the VnV Plan.

\begin{table}[H]
\centering
\caption{Nonfunctional Requirements Traceability Matrix}
\label{tab:trace-nfr}
\resizebox{\textwidth}{!}{
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
\textbf{Requirement ID} & \textbf{T--NF1} & \textbf{T--NF2} & \textbf{T--NF3} &
\textbf{T--NF4} & \textbf{T--NF5} & \textbf{T--NF6} \\ \hline
PR--SL1   & X &   &   &   &   &   \\ \hline
PR--RFT1  &   & X &   &   &   &   \\ \hline
PR--RFT2  &   & X &   &   &   &   \\ \hline
PR--RFT3  &   & X &   &   &   &   \\ \hline
SR--INT5  &   & X &   &   &   &   \\ \hline
UH--EU1   &   &   & X &   &   &   \\ \hline
LF--AR2   &   &   & X &   &   &   \\ \hline
UH--UP3   &   &   & X &   &   &   \\ \hline
LF--SR2   &   &   & X &   &   &   \\ \hline
PR--PA1   &   &   &   & X &   &   \\ \hline
FR12      &   &   &   & X &   &   \\ \hline
PR--SC1   &   &   &   &   & X &   \\ \hline
PR--SC2   &   &   &   &   & X &   \\ \hline
PR--SC3   &   &   &   &   & X &   \\ \hline
SR--AC6   &   &   &   &   & X &   \\ \hline
SR--IM1   &   &   &   &   & X &   \\ \hline
SR--AU1   &   &   &   &   & X &   \\ \hline
MS--MR1   &   &   &   &   &   & X \\ \hline
MS--MR2   &   &   &   &   &   & X \\ \hline
MS--MR3   &   &   &   &   &   & X \\ \hline
MS--MR4   &   &   &   &   &   & X \\ \hline
MS--MR5   &   &   &   &   &   & X \\ \hline
MS--MR6   &   &   &   &   &   & X \\ \hline
\end{tabular}
}
\end{table}

The tests listed in this section were designed to provide verification evidence
for the nonfunctional requirements in the SRS. An ``X'' indicates that the
corresponding test case contributes evidence for that requirement. Note that
evidence may include Pass, Partial, or Pending outcomes as reported in the
nonfunctional requirements evaluation section.

\section{Trace to Modules}		
Table~\ref{tab:trace} presents the traceability between the system test cases and the software modules defined in the system architecture. The table indicates which test cases provide verification evidence for each module implemented in the system.
\begin{table}[H]
\centering
\caption{Traceability Between Modules and System Test Cases}
\label{tab:trace}
\resizebox{\textwidth}{!}{
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
\textbf{Module} & \textbf{T-AC-1} & \textbf{T-AC-2} & \textbf{T-AC-3} & \textbf{T-AC-4} & \textbf{T-AC-5} & \textbf{T-AC-6} & \textbf{T-AC-7} & \textbf{T-DM-1} & \textbf{T-DM-2} & \textbf{T-DM-3} & \textbf{T-DM-4} & \textbf{T-DM-5} & \textbf{T-VR-1} & \textbf{T-VR-2} & \textbf{T-VR-3} & \textbf{T-VR-4} & \textbf{T-VR-5} & \textbf{T-VR-6} \\ \hline
M2  &   &   &   &   &   &   &   &   &   &   &   &   &   &   &   & X &   &   \\ \hline
M3  &   &   &   &   & X &   & X &   &   & X &   & X &   &   & X & X &   & X \\ \hline
M4  &   &   &   &   &   & X &   & X & X & X &   &   &   &   &   &   &   &   \\ \hline
M5  & X & X &   &   &   &   & X &   &   &   &   &   &   &   &   &   &   &   \\ \hline
M6  &   &   & X & X &   & X &   & X &   &   &   &   &   &   &   &   &   &   \\ \hline
M7  & X &   &   &   &   &   &   &   &   &   &   &   &   &   &   &   &   &   \\ \hline
M8  &   &   &   &   &   &   &   &   & X &   &   &   &   &   &   &   &   &   \\ \hline
M9  &   &   &   &   &   &   &   & X &   &   &   &   &   &   &   &   &   & X \\ \hline
M10 &   &   &   &   &   &   &   &   &   &   & X & X &   &   & X & X & X & X \\ \hline
M11 &   &   &   &   &   &   &   &   &   & X &   &   & X &   &   &   &   &   \\ \hline
M12 &   &   &   &   &   &   &   &   &   &   &   &   & X & X & X & X &   & X \\ \hline
M14 &   &   &   &   &   & X &   &   & X & X &   & X &   &   & X &   &   &   \\ \hline
M15 &   &   &   &   &   &   &   &   & X &   &   &   &   &   &   &   &   &   \\ \hline
M16 &   &   &   &   &   &   &   &   &   & X &   &   & X & X &   &   &   &   \\ \hline
M17 &   &   &   &   &   & X &   &   & X & X & X &   & X &   &   &   & X &   \\ \hline
M18 &   &   &   &   &   &   &   &   &   &   & X &   &   &   &   &   & X &   \\ \hline
M19 &   &   &   &   &   &   &   & X &   &   &   &   &   &   &   &   &   &   \\ \hline
\end{tabular}
}
\end{table}
	

\section{Code Coverage Metrics}
The following report is automatically generated by pytest. We obtained a total coverage of 73\%. The actual coverage should be slightly higher since some files that contain no logic are being counted towards the percentage (i.e. \href{https://github.com/thaafei/DomainX/blob/main/src/backend/api/database/edit_history/views.py}{edit\_history/views}).

\begin{landscape}
\centering
\begin{longtable}{|p{10cm}|c|c|c|c|}
    \caption{Backend Code Coverage Report} \\
    \hline
    \textbf{File} & \textbf{Statements} & \textbf{Missing} & \textbf{Excluded} & \textbf{Coverage} \\ 
    \hline
    \endfirsthead

    \hline
    \textbf{File} & \textbf{Statements} & \textbf{Missing} & \textbf{Excluded} & \textbf{Coverage} \\ 
    \hline
    \endhead
      \textbf{\path{src/backend/api/database/backup_logs/admin.py}} & 1 & 0 & 0 & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/backup\_logs/models.py}} & 12 & 1 & 0  & 92\% \\ \hline
      \textbf{\path{src/backend/api/database/backup\_logs/views.py}} & 1 & 1 & 0 & 0\% \\ \hline
      \textbf{\path{src/backend/api/database/domain/models.py}} & 17 & 0 & 0 & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/domain/serializers.py}} & 16 & 1 & 0  & 94\% \\ \hline
      \textbf{\path{src/backend/api/database/domain/views.py}} & 51 & 15 & 0  & 71\% \\ \hline
      \textbf{\path{src/backend/api/database/edit\_history/admin.py}} & 1 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/edit\_historymodels.pyy}} & 16 & 1 & 0  & 94\% \\ \hline
      \textbf{\path{src/backend/api/database/edit\_historyviews.py}}  & 1 & 1 & 0  & 0\% \\ \hline
      \textbf{\path{src/backend/api/database/libraries/models.py}} & 38 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/libraries/serializers.py}}  & 35 & 2 & 0  & 94\% \\ \hline
      \textbf{\path{src/backend/api/database/libraries/views.py}}  & 67 & 1 & 0  & 99\% \\ \hline
      \textbf{\path{src/backend/api/database/library\_metric\_values/admin.py}}  & 8 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/library\_metric\_values/models.py}}  & 14 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/library\_metric\_values/serializers.py}}  & 12 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/library\_metric\_values/views.py}}  & 153 & 7 & 0  & 95\% \\ \hline
      \textbf{\path{src/backend/api/database/metrics/admin.py}}  & 6 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/metrics/models.py}}  & 15 & 1 & 0  & 93\% \\ \hline
      \textbf{\path{src/backend/api/database/metrics/serializers.py}}  & 10 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/database/metrics/views.py}}  & 53 & 28 & 0  & 47\% \\ \hline
      \textbf{\path{src/backend/api/database/services.py}}  & 241 & 129 & 0  & 46\% \\ \hline
      \textbf{\path{src/backend/api/models.py}}  & 5 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/serializers.py}}  & 4 & 4 & 0  & 0\% \\ \hline
      \textbf{\path{src/backend/api/services/github\_http.py}}  & 67 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/api/tasks.py}}  & 109 & 19 & 0  & 83\% \\ \hline
      \textbf{\path{src/backend/api/utils/analysis.py}}  & 26 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/manage\_local.py}}  & 55 & 55 & 0  & 0\% \\ \hline
      \textbf{\path{src/backend/users/auth.py}}  & 11 & 5 & 0  & 55\% \\ \hline
      \textbf{\path{src/backend/users/backends.py}}  & 15 & 15 & 0  & 0\% \\ \hline
      \textbf{\path{src/backend/users/models.py}}  & 14 & 0 & 0  & 100\% \\ \hline
      \textbf{\path{src/backend/users/permissions.py}}  & 7 & 7 & 0  & 0\% \\ \hline
      \textbf{\path{src/backend/users/serializers.py}}  & 28 & 5 & 0  & 82\% \\ \hline
      \textbf{\path{src/backend/users/views/auth\_views.py}}  & 131 & 32 & 0  & 76\% \\ \hline
      \textbf{\path{src/backend/users/views/profile.py}}  & 25 & 12 & 0  & 52\% \\ \hline
      \textbf{Total}  & 1265 & 342 & 0  & 75\% \\ \hline
\end{longtable}
\end{landscape}
\bibliographystyle{plainnat}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable?
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?\\

  \textbf{Haniye:} A minor challenge during this deliverable was ensuring that
    the tests described in the report aligned with the original VnV Plan while
    also reflecting the current implementation of the system. Some features had
    changed during development, which made it necessary to adjust how certain
    tests were documented. Feedback from the teaching assistant helped clarify
    how the tests should be structured, allowing the report to accurately
    represent the implemented functionality.

    \textbf{Fei:} Setting up the testing frameworks was complete, due to the way our project repository was structured. Our code also wasn't as modularized as intended, so many unit tests had to have a lot of mocking in place. The way I resolved them was just adding the testing frameworks earlier, so there was more time to deal with unexpected issues, as opposed to having to cram it all in this week. \\

    \textbf{Ghena:} A significant challenge during this deliverable was ensuring the AHP Ranking Module (M11) was implemented correctly to avoid any methodology misunderstandings. To resolve this, the team held a focused meeting with the supervisor to walk through the exact calculation requirements and conducted a thorough review of the assigned research paper.

    \textbf{Awurama}:  Some planned tests were not feasible in Rev0 (domain filter no-op, HTTP 429 not reproducible, backup/restore requires DB-level procedure). We reported what we could verify, marked missing items as \emph{Not tested}/\emph{Pending}, and listed clear next steps. Manual stopwatch timing also adds reaction-time error, so we documented the method and treated results as conservative upper bounds.

  \item Which parts of this document stemmed from speaking to your client(s) or
  a proxy (e.g. your peers)? Which ones were not, and why?\\

  \textbf{Haniye:} Some parts of this document were influenced by discussions
    with the project supervisor. For example, the bulk data upload feature was removed from the project scope after supervisor feedback
    indicated that it would not be necessary for the final tool. The
    supervisor also suggested removing the public sign-up feature and
    instead allowing a Super Admin to create user accounts directly, with
    users updating their password afterward.

  \textbf{Fei:} N/A\\

  \textbf{Ghena:} All of the changes made due to testing came from the our client/stackholder meetings. However The specific direct mapping (e.g., tracing T–AC–1 to M5 and M7) didn't stem from those meetings.

  \textbf{Awurama}: The usability section (T--NF3) stems from a proxy user worksheet with task ratings and comments. The remaining NFR sections were primarily tool/code/CI-based verification (performance timing, offline fault injection and recovery, repo-field spot checks, security configuration review, CI maintainability evidence), so they did not require client input in Rev0.

  \item In what ways was the Verification and Validation (VnV) Plan different
  from the activities that were actually conducted for VnV?  If there were
  differences, what changes required the modification in the plan?  Why did
  these changes occur?  Would you be able to anticipate these changes in future
  projects?  If there weren't any differences, how was your team able to clearly
  predict a feasible amount of effort and the right tasks needed to build the
  evidence that demonstrates the required quality?  (It is expected that most
  teams will have had to deviate from their original VnV Plan.)\\

  \textbf{Haniye:} Most of the verification and validation activities followed
    the original VnV Plan. Some small differences occurred due to time
    constraints and changes in project priorities. For example, the bulk data
    upload feature was removed from the project scope based on supervisor
    feedback, so its related test was not implemented.
    Some tests were also influenced by issues discovered during deployment.
    For instance, while deploying the system, GitStats initially did not run
    correctly on the server and the analysis process continued for an
    unexpectedly long time. During debugging, the request timeout was reduced,
    which allowed us to observe the system’s failure message and verify that
    the application handled the error properly.

    In future projects, some of these adjustments could be anticipated by
    planning additional tests for integration and deployment scenarios.

  \textbf{Fei:} The changes I had to make to the unit test portion was the modules. As we developed the tool, we ended up condensing a few modules together since that made more sense during the development. This just meant combining the related unit tests of the combined modules into one. For future projects, I don't think we can mitigate it completely. Since we designed the project before development, during development new insights arises which results in changes to the theoretical plan.\\

  \textbf{Ghena:} The final VnV activities deviated from the plan primarily because the AHP Calculation Module (M11) required restructuring to align with the methodology in the assigned research paper, replacing an initial simplified model. These changes could have been avoided had the module been revised more properly during the initial design phase. Additionally, features like Excel bulk upload (FR9) were removed to prioritize core stability. While some scope reductions are manageable, predicting the future requirements of this project proved difficult and would remain a challenge in future iterations.

  \textbf{Awurama}: Rev0 deviated from the plan mainly due to feasibility and environment constraints: performance used available domains (2 and 10 libraries) with manual timing instead of 5/10/20/40 and automated measurement; reliability used offline-mode fault injection since 429 was not reproducible and caching/warnings were not observable; computational accuracy captured tool priorities plus a GitHub spot check but did not complete the full manual AHP computation with $2\%$ error checks; security verified settings/auth/logging but did not confirm lockout/session timeout (no explicit configuration found); maintainability used CI evidence but coverage did not meet the planned target and lint automation was not observed. These changes occurred because data, reproducible fault triggers, and infra access were limited in Rev0. In future projects, we can anticipate these risks and plan mitigations (early dataset prep, instrumentation for timing, fault-injection hooks, and explicit Rev0 vs.\ Rev1 evidence expectations).

\end{enumerate}

\end{document}
